---
title: "Sean Sears Activity 1"
author: "Sean Sears"
date: '2019-09-18'
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Research Interest
The focus of my research is on understanding the __perceived__ barriers to metropolitan freight congestion in Canada's major regions. Using qualitative methodologies, specifically a grounded theory emergent approach, interviews with 28 industry experts and government officials were analyzed to determine what the main barriers were perceived to be  __at the time__ of the interviews. The first paper of my sandwich thesis,  _Understanding the Perceived Barriers to Freight Congestion in Canada's Major Metropolitan Regions: A Grounded Theory Approach_ is in draft. The second paper,  _Understanding the Gaps Between Industry and Government Perceptions to the Barriers of Goods Movements in Canada’s Major Regions: A Dual Grounded Theory Approach_ much of the analysis is ready to be finished and prepared for visualization and discussion. The second paper uses a somewhat novel approach by employing two separate GTAs to develop separate emergent theories for the two groups assessed; the theories are then compared and contrasted to develop an understanding of where industry and government see eye-to-eye, and where there are discrepancies in perception.

#Favourites
##Favourite Music
1. Never Again, Bahamas
2. Stronger Than That, Bahamas
3. All The Time, Bahamas
4. Changing of the Seasons, Two Door Cinema Club
5. Yellow, Coldplay

## Favourite Equation
$$ E=mc^2 $$

##Favourite Artists

Artist | Accomplishment  
- | -
Bahamas  | Canadian Music Award (CMA)  
Coldplay | Grammy  
San Cisco | None  
Arkells | CMA
Rex Orange County | None

#A Chunk of Code
The following chunk of code will plot the equation of a straight line wherein the Y-intercept is _-50_ with a gradient of _3_, for x-values of _-50_ through _50_.
```{r This makes a plot}
b <- -50
x <- c(-50:50)
m = 3
plot(y=m*x+b, x=x)
```
